Hypertension and microbiome

### 2019-01-25 articletwo.Rmd
Minor

```{r alphabeta definitions}
dset.alpha <- meta.merge.alphadiversity(pseq.species)
alphadiversity <- list(
    min = calculateglm(dset.alpha, modelstring = "%s ~ BL_AGE + SEX  + diversities_shannon"),
    max = calculateglm(dset.alpha, modelstring = "%s ~ BL_AGE + SEX + BMI + CURR_SMOKE + Q57X + DIAB + BL_USE_RX_C03 + BL_USE_RX_C07 + BL_USE_RX_C08 + BL_USE_RX_C09  + diversities_shannon"))
diversities <- mergediversities(alphadiversity, adonis.species)

betadiversity$min$model_1 %>% select(term, R2)
betadiversity$max$model_1 %>% select(term, R2)

```

@@

```{r Write figure 2}
fig1head <- "alpha beta figure"
fig1foot <- ""
writeimage(doc, 1, "cache/alpha-beta.png", fig1head, fig1foot)
```

>>>>

```{r alphabeta definitions}
dset.alpha <- meta.merge.alphadiversity(pseq.species)
alphadiversity <- list(
    min = calculateglm(dset.alpha, modelstring = "%s ~ BL_AGE + SEX  + diversities_shannon"),
    max = calculateglm(dset.alpha, modelstring = "%s ~ BL_AGE + SEX + BMI + CURR_SMOKE + Q57X + DIAB + BL_USE_RX_C03 + BL_USE_RX_C07 + BL_USE_RX_C08 + BL_USE_RX_C09  + diversities_shannon"))
diversities <- mergediversities(alphadiversity, adonis.species)
```

@@

```{r Write figure 1}
fig1head <- "alpha beta figure"
fig1foot <- ""
writeimage(doc, 1, "cache/alpha-beta.png", fig1head, fig1foot)
```
